---
title: "GDAT 622 Investigation 6"
author: "Pavan Hothi"
date: "7/5/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("conflicted",   
    "data.table",    
    "dplyr",         
    "drat",          
    "dtplyr",       
    "here",
    "igraph",       
    "igraphdata",    
    "intergraph",    
    "NetData", 
    "rtweet",
    "statnet"        
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
  
  
  if (!is.element("networkdata", installed.packages()[, 1])) {
    addRepo("schochastics")
    install.packages("networkdata")
  }
  library(
    "networkdata",
    character.only = TRUE,
    quietly = TRUE,
    verbose = FALSE
  )
}

set_here()


options(show.signif.stars = FALSE)
options(digits = 4)
```


I will be pulling and looking at the last 500 tweets of Nike. 
```{r}
get_timeline(c("Nike"), n = 500) -> nike

```


Keeping only the reply screen name and tweet text replied with. 
```{r}
nike %>%
  select(., reply_to_screen_name, text) %>% 
  na.omit(.) %>%
  distinct(.) -> nike

```


Plot
```{r}
graph.data.frame(nike) -> nike_graph
plot(nike_graph, vertex.label = NA)

```


Pull Nike's following list in order to better understand interactions. 
```{r}
get_friends(415859364) -> nike_following

```


Get following lists of some of Nike's following.
```{r}
get_friends(23151437) -> following1
get_friends(2511477648) -> following2
get_friends(21870081) -> following3
get_friends(184241421) -> following4
get_friends(69347129) -> following5

```


Combine following lists
```{r}
bind_rows(nike_following, following1, following2, following3, following4, following5) -> following_combined

```


Plot
```{r}
graph.data.frame(following_combined) -> following_combined_graph
plot(following_combined_graph)

```

Look up one of the connections
```{r}
lookup_users("71026122")
```
Funnily enough, it appears that the McDonald's twitter account has some connections to some of the same accounts as Nike's twitter. Wouldn't have expected a fast food chain to have connections with an athletic company. 
